Javelins with hyper3 objects

### 2022-04-18 inst/javelin.Rmd
consistentification of attemptstable2supp3()

```{r}
a <- read.table("javelin.txt",header=TRUE)
a
a <- t(a)
a
o <- NULL
for(i in seq_len(ncol(a))){
  jj <- as.numeric(a[,i])
  names(jj) <- rep(colnames(a)[i],length(jj))
  o <- c(o,jj)
}
o <-sort(o,na.last=TRUE,decreasing=TRUE)
o
names(o)
plot(o)
```

>>>>

```{r,label=loadjavelinandconvert}
a <- read.table("javelin.txt",header=TRUE)
a
o <- attemptstable2supp3(a,decreasing=TRUE,give.supp=FALSE)
o
```

Plot the data in visual form:

```{r, label=plotjav}
n <- length(levels(as.factor(names(o))))
plot(o,pch=16,col=rainbow(n)[as.factor(names(o))])
legend("topright",pch=16,col=rainbow(n),legend=levels(as.factor(names(o))))
```
